% This is based on LLNCS.dem the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
% Modified by Gabriele Bleser, January 2013
% Modified by Oliver Wasenmüller, March 2016
% 
% This is the Latex main document. If you need additional packages, 
% you can insert them here. Otherwise you should not modify this.
% Provide your contribution in a separate file, such as mypaper.tex.
% All contributions will be included here.
%

\documentclass{llncs}

% Include your packages here
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{subfiles}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{url}
\graphicspath{ {images/} }

%\usepackage{makeidx}  % allows for indexgeneration

\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads
%
\begin{titlepage}
\centering
\Large Proceedings of Seminar and Project\\\vspace{1cm} 
\LARGE TITLE\\\vspace{1cm} 
\large SEMESTER\\
\vspace{1cm}
\large Oliver Wasenm\"uller and Prof. Didier Stricker\\

\large Department Augmented Vision\\ University of Kaiserslautern and DFKI GmbH
\end{titlepage}

\chapter*{Introduction}
%
%To be filled by course organizer
The seminar and project TITLE (INF-XX-XX-S-X, INF-XX-XX-L-X) are continuative courses based on and applying 
the knowledge taught in the lectures 3D Computer Vision (INF-73-51-V-7) and Computer Vision: Object and People Tracking (INF-73-52-V-7). The goal of the project is to research, design, implement and evaluate
algorithms and methods for tackling computer vision problems.
The seminar is more theoretical. Its educational objective is to train the ability to become acquainted 
with a specific research topic, review scientific articles and give a comprehensive presentation supported by media.

In the XXX semester XXX, XXX projects addressing XXX were developed.
Moreover, XXX seminar works addressed XXX.
The results are documented in these proceedings.


\section*{Organisers and supervisors}
The courses are organised by the Department Augmented Vision (\url{http://ags.cs.uni-kl.de}), more specifically by:
\begin{description}
	\item[Oliver Wasenm\"uller]
	\item[Prof. Dr. Didier Stricker] 
\end{description}
In the XXX semester XXX, the projects were supervised by the following department members:
\begin{description}
	\item[NAME]
\end{description}

\vspace{1cm}
\begin{flushright}\noindent
MONTH YEAR
\end{flushright}
%

%
%\tableofcontents
%
\mainmatter              % start of the contributions
%
\input{mypaper}
%
\end{document}
